ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-09 pyked.tex
Add paragraph to conclusion about examples

>>>>

Finally, we presented several examples of the use of \pk{} to interpret and interact with data
stored in \ck{} files. Both examples are also available online as Jupyter Notebook files in the
GitHub repository and in the Supplementary Material. The first example involved the simulation of a
rapid compression machine experiment, including the facility-specific effects that are critical to
accurately predict ignition delay experiments. The second example demonstrated the use of built-in
Python libraries to automatically run simulations of several shock tube experiments in parallel,
with initial conditions loaded directly from the \ck{} file.
